### 2007-01-17 Documentation/part1.tex
*** empty log message ***

FOR WW MYSELF: TOUR ITSELF (+EXAMPLE FILE) TO BE UPDATED (VALUES MAY HAVE CHANGED DUE TO AEDL FILE DEFINITION
CHANGES ETC. ALSO EXPERIMENT (OLD) NUFACT DOES NOT EXIST ANYMORE. AND: SOME ERROR IN THIS OLD
NUFACT-FILE [WW].

CHECK: GLBSETPROJECTION REALLY USED WITH GLB\_FIXED FOR DENSITY PARAMS? IS NFSTANDARD USED?
(QUESTIONS FOR WW MYSELF!)

In this first chapter, we show a \GLOBES\ tour illustrating the
main features of \GLOBES . The complete example  
can be found as {\tt example-tour.c} in the \verb+example+ subdirectory 
of your \GLOBES\ distribution.
The output is written to {\tt stream}, which can be either {\tt stdout},
or a file. Details about how to use \GLOBES\ with C can found in \Chapt~\ref{chapt:gettingstarted} and the following chapters.
You can also find a summary of the most important \GLOBES\ $\chi^2$-functions in \tabl{stdfunctions}. Note that this chapter
can be skipped without loss of relevant information.

@@

glb\_params starting\_values = glbAllocParams();\\

@@

Oscillation probabilities in vacuum: 1->1: 0.999953 1->2: 2.69441e-05 1->3: 1.98019e-05 \\
Oscillation probabilities in matter: 1->1: 0.999965 1->2: 2.02573e-05 1->3: 1.49021e-05 

@@

chi2 with systematics only: 22.3984

@@

This we would have from the CP-even appearance channel only: 21.6223

@@

The sum over all rules gives again: 22.3984

@@

chi2 with correlations: 2.1038 \\

@@

0.542002 0.0193698 0.747915 1.77688 6.66156e-05 0.00200817 \\
1.00434 \\
Iterations: 1693 \\

@@

chi2 with correlations other than with deltacp: 4.32831 

@@

chi2 with correlation only with deltacp: 2.80651 

@@

chi2 with statistics only: 39.143

@@

  glbDefineParams(starting\_values,theta12,theta13,theta23, \\

@@

  glbSetCentralValues(starting\_values);\\

@@

  chi2=glbChiAll(starting\_values,minimum,GLB\_ALL);\\ 

@@

chi2 at minimum: 6.20025 \\

@@

0.591812 0.0264717 0.72763 1.08709 8.0004e-05 -0.00206094 \\
0.970685  \\
Iterations: 1946 \\

@@

 glbFreeParams(starting\_values);\\

@@

 starting\_values = glbAllocParams(); \\

@@

 glb\_params minimum2 = glbAllocParams(); 

@@

 chi2 with systematics for all exps: 31.0797

@@

chi2 with systematics for 3000km: 22.3984 \\
chi2 with systematics for 7500km: 8.68131 \\

@@

chi2 with correlations for 3000km: 2.1038 \\
0.542002 0.0193698 0.747915 1.77688 6.66156e-05 0.00200817 \\ 
1.00434 1 \\
Iterations: 1693 \\

@@

chi2 with correlations for 7500km: 1.08421 \\
0.557356 0.0193698 0.771359 4.77751 7.00762e-05 0.00200105 \\
1 1.01517 \\
Iterations: 661 \\

@@

chi2 with correlations for combination: 3.90835  \\
0.544432 0.0193698 0.770175 1.78502 6.61621e-05 0.00200303 \\ 
1.00431 1.03679 \\
Iterations: 1636 \\

@@

The sum of the two chi2s is 3.18801, whereas the total chi2 is 3.90835!

@@

Now find the $\mathrm{sgn}(\ldm)$-degeneracies for both individual
experiments and test if they are still there in the combination of the

@@

  glbSetDensityParams(starting\_values,1.0,GLB\_ALL); \\
  glbSetCentralValues(starting\_values);\\

@@

  chi2=glbChiAll(starting\_values,minimum,0); \\ 

@@

  chi2b=glbChiAll(starting\_values,minimum2,1);  \\
  \mbox{fprintf(stream,"$\backslash$nchi2 at minimum, L=7500km: \%g \\ $\backslash$n",chi2b);} \\
  glbPrintParams(stream,minimum2);  \\

@@

  chi2b=glbChiAll(minimum2,minimum2,GLB\_ALL); \\
  fprintf(stream,"$\backslash$nchi2 for combination at minimum of Exp. 2: \\
  glbPrintParams(stream,minimum2);  

@@

chi2 at minimum, L=3000km: 6.71794 \\
0.591497 0.0257396 0.729058 1.11537 7.98867e-05 -0.00206005 \\
0.970499 1 \\
Iterations: 2104\\

@@

chi2 at minimum, L=7500km: 47.1013 \\
0.590347 0.0018489 0.768372 0.984827 8.23415e-05 -0.00204588 \\
1 0.780995 \\
Iterations: 1270\\
chi2 for combination at minimum of Exp. 1: 70.6353 \\
0.607988 0.0165985 0.767682 1.41422 8.44573e-05 -0.00204853 \\
0.96147 1.1831 \\
Iterations: 1549 \\
chi2 for combination at minimum of Exp. 2: 70.6357 \\
0.608454 0.0165823 0.767757 1.41481 8.43864e-05 -0.00204853 \\
0.961129 1.18304 \\
Iterations: 1447 

@@

 glbFreeParams(starting\_values); \\

@@

 glbFreeParams(minimum2); \\

@@

In many cases, one can find the exact position of the 
$\mathrm{sgn}(\ldm)$-degeneracy with \GLB{ChiAll}, where one starts 
the local minimizer at the suspected position 
and lets it run into the minimum.  The following code excerpt  corresponds to finding the degenerate solution for the example on
  page~\pageref{ex:corrth13dcp}, and it is from {\tt example3.c}: 
\begin{quote}
{\tt
{\footnotesize
  /* Set starting vales to suspected position at opposite sign of ldm */ \\
  \mbox{glbDefineParams(starting\_values,theta12,theta13,theta23,deltacp,sdm,-ldm);} \\
  glbSetDensityParams(starting\_values,1.0,GLB\_ALL); \\
  \\
  /* Set input errors for external input, where some information on ldm \\
   \hspace*{0.5cm} is imposed in order to avoid falling into the right-sign solution */ \\
  glbDefineParams(input\_errors,theta12*0.1,0,0,0,sdm*0.1,ldm/3); \\ 
  glbSetDensityParams(input\_errors,0.05,GLB\_ALL); \\
  \\
  glbSetCentralValues(starting\_values); \\
  glbSetInputErrors(input\_errors); \\
  \\
  /* Localize degenerate solution by minimization over all parameters */ \\
  double CL=glbChiAll(starting\_values,deg\_pos,GLB\_ALL); \\
   \\
  \mbox{/* Now: CL is the chi2 of the deg.~solution and deg\_pos the position */} 
}}
\end{quote}

>>>>

In this first chapter, we show a \GLOBES\ tour illustrating the
main features of \GLOBES . The complete example  
can be found as {\tt example-tour.c} in the \verb+example+ subdirectory 
of your \GLOBES\ distribution.
The output is written to {\tt stream}, which can be either {\tt stdout},
or a file.\footnote{Note that the output in this section can be slightly
different from yours depending on the current version of the 
probability engine, systematics implementation, and \AEDL\ file used.}
Details about how to use \GLOBES\ with C can found in \Chapt~\ref{chapt:gettingstarted} and the following chapters.
You can also find a summary of the most important \GLOBES\ $\chi^2$-functions in \tabl{stdfunctions}. Note that this chapter
can be skipped without loss of relevant information.

@@

glb\_params central\_values = glbAllocParams();\\

@@

Oscillation probabilities in vacuum: 1->1: 0.999955 1->2: 2.58628e-05 1->3: 1.92142e-05 \\
Oscillation probabilities in matter: 1->1: 0.999965 1->2: 2.01364e-05 1->3: 1.49644e-05 

@@

chi2 with systematics only: 22.433

@@

This we would have from the CP-even appearance channel only: 21.1569

@@

The sum over all rules gives again: 22.433

@@

chi2 with correlations: 1.99794 \\

@@

0.541226 0.0193698 0.746156 1.74968 6.64399e-05 0.00200514 \\
1.00341 \\
Iterations: 1988 \\

@@

chi2 with correlations other than with deltacp: 4.02974  

@@

chi2 with correlation only with deltacp: 2.72943

@@

chi2 with statistics only: 37.9736

@@

  glbDefineParams(central\_values,theta12,theta13,theta23, \\

@@

  glbSetCentralValues(central\_values);\\

@@

  chi2=glbChiAll(central\_values,minimum,GLB\_ALL);\\ 

@@

chi2 at minimum: 4.2137 \\

@@

0.585006 0.0275073 0.725679 1.05251 7.80256e-05 -0.00191273  \\
0.979049  \\
Iterations: 3184

@@

 glbFreeParams(central\_values);\\

@@

 central\_values = glbAllocParams(); \\

@@

@@

 chi2 with systematics for all exps: 30.5678

@@

chi2 with systematics for 3000km: 22.433 \\
chi2 with systematics for 7500km: 8.1348 \\

@@

chi2 with correlations for 3000km: 1.99794 \\
0.541226 0.0193698 0.746156 1.74968 6.64399e-05 0.00200514 \\ 
1.00341 1  \\
Iterations: 1988 \\

@@

chi2 with correlations for 7500km: 0.803787 \\
0.556503 0.0193698 0.771812 4.75971 7.00813e-05 0.0020012 \\ 
1 1.01201 \\
Iterations: 798 \\

@@

chi2 with correlations for combination: 3.68133 \\
0.543335 0.0193698 0.77004 1.75576 6.59505e-05 0.00199913 \\ 
1.00333 1.03269 \\
Iterations: 2187 \\

@@

The sum of the two chi2s is 2.80173, whereas the total chi2 is 3.68133!

@@

Now find the $\mathrm{sgn}(\ldm)$-degeneracy for the neutrino factory
at the short baseline and test if it is still present in the combination of the

@@

  glbSetDensityParams(central\_values,1.0,GLB\_ALL); \\
  glbSetCentralValues(central\_values);\\

@@

  chi2=glbChiAll(central\_values,minimum,0); \\ 

@@

@@

@@

chi2 at minimum, L=3000km: 4.82021  \\
0.584568 0.026488 0.727714 1.09015 7.78747e-05 -0.00191163 \\ 
0.978867 1 \\
Iterations: 3298 \\

@@

chi2 for combination at minimum of Exp. 1: 59.4879 \\
0.599908 0.0172467 0.768342 1.39186 8.198e-05 -0.00189508 \\ 
0.970733 1.17125 \\
Iterations: 2327 \\

@@

 glbFreeParams(central\_values); \\

@@

@@

In many cases, one can find the exact position of the 
$\mathrm{sgn}(\ldm)$-degeneracy with \GLB{ChiAll}, where one starts 
the local minimizer at the suspected position 
and lets it run into the minimum.  The following code excerpt  corresponds to finding the degenerate solution for the example on
  page~\pageref{ex:corrth13dcp}, and it is from {\tt example3.c}: 
\begin{quote}
{\tt
{\footnotesize
  /* Set starting vales to suspected position at opposite sign of ldm */ \\
  \mbox{glbDefineParams(central\_values,theta12,theta13,theta23,deltacp,sdm,-ldm);} \\
  glbSetDensityParams(central\_values,1.0,GLB\_ALL); \\
  \\
  /* Set input errors for external input, where some information on ldm \\
   \hspace*{0.5cm} is imposed in order to avoid falling into the right-sign solution */ \\
  glbDefineParams(input\_errors,theta12*0.1,0,0,0,sdm*0.1,ldm/3); \\ 
  glbSetDensityParams(input\_errors,0.05,GLB\_ALL); \\
  \\
  glbSetCentralValues(central\_values); \\
  glbSetInputErrors(input\_errors); \\
  \\
  /* Localize degenerate solution by minimization over all parameters */ \\
  double CL=glbChiAll(central\_values,deg\_pos,GLB\_ALL); \\
   \\
  \mbox{/* Now: CL is the chi2 of the deg.~solution and deg\_pos the position */} 
}}
\end{quote}
